Do NBA Teams Avoid Trading within Their Own Division?^[We appreciate feedback we received on this paper from Skye Bender-deMoll, Pavel Krivitsky and David Schaefer.]

### 2022-01-05 Manuscript.Rmd
Add table-making Rmd

```{r model1-table-short, eval=FALSE}
 withr::with_options(
   list(knitr.kable.NA = ""),
   readRDS("model1-table-short.rds") |>
     knitr::kable(
       caption = "**Valued ERGM fitted to pooled seasonal data**. The table excludes seasonal constants, complete table is presented in the Appendix.",
       align = "lrrrr"
     )
 )
```

>>>>

```{r model1-table-short}
 withr::with_options(
   list(knitr.kable.NA = ""),
   readRDS("model1-table-short.rds") |>
     knitr::kable(
       caption = "**Valued ERGM fitted to pooled seasonal data**. The table excludes seasonal constants, complete table is presented in the Appendix.",
       align = "lrrrr"
     )
 )
```
